Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:07	11:08:35	(Mon 7.Sep)

\Fig{oversampling_mosaic_bounds_beta} illustrates which $\beta$-value LCA prefers for different regions in the image of the cross. Red marker lines are used to pinpoint the cut line and location of the anchor. Observe that in the anchor region only rectangular windows are used, which is the reason for the anchor resolution being measure to the same value regardless of the upper bound of $\beta$ in \Fig{oversampling_mosaic_bounds}.

@@

What is the best set of Kaiser windows to use with LCA, and how much should they be steered?

To investigate this we constructed large and equally sized window databases containing windows with varied upper boundaries for $\beta$ and $\phi$. As lower boundaries we chose $\beta=0$ and $\phi=\pm0^\circ$, which includes the rectangularly weighted DAS image. The images produced are shown in \Fig{oversampling_mosaic_bounds}.

>>>>

\Fig{oversampling_mosaic_bounds_beta} illustrates which $\beta$-value LCA prefers for different regions in the image of the cross. Red marker lines are used to pinpoint the cut line and location of the anchor. Observe that in the anchor region only rectangular windows are used, which is the reason for the anchor resolution being measured to the same value regardless of the upper bound of $\beta$ in \Fig{oversampling_mosaic_bounds}.

@@

What is the best set of Kaiser windows to use with LCA, and how much should they be steered? To investigate this we constructed large and equally sized window databases containing windows with varied upper boundaries for $\beta$ and $\phi$. As lower boundaries we chose $\beta=0$ and $\phi=\pm0^\circ$, which includes the rectangularly weighted DAS image. The images produced are shown in \Fig{oversampling_mosaic_bounds}.
